Bayesian Rate Estimation

### 2012-09-04 many.tex
Added a few lines to discussion.

Furthermore, in a practical application there could be multiple classes of events, not just foreground and background.  For example, we are not necessarily interested in the rate of gravitational-wave signals per se, but separately in the rate of signals from mergers of binary neutron stars and binary black holes -- populations that may sometimes be difficult to distinguish.  Our approach is readily extendable to this particular complication, however.  Note that it is symmetric with respect to foreground and background events (as expected, since one physicist's background is another physicist's foreground).  We could relabel foreground and background events into other competing event classes, and further classes could be added in a straightforward way.

>>>>

Furthermore, in a practical application there could be multiple classes of events, not just foreground and background.  For example, we are not necessarily interested in the rate of gravitational-wave signals per se, but separately in the rate of signals from mergers of binary neutron stars and binary black holes -- populations that may sometimes be difficult to distinguish.  Our approach is readily extendable to this particular complication, however.  Note that it is symmetric with respect to foreground and background events (as expected, since one physicist's background is another physicist's foreground).  We could relabel foreground and background events into other competing event classes, and further classes could be added in a straightforward way.  However, the ability to distinguish classes relies on different distributions of their statistics.  In general, rankings may need to be extended to include other statistics in addition to the signal ``loudness'' statistic in order to indicate both event significance and the probability of event attribution to a particular class.
